A Machine Learning Approach to MLB Catcher Framing

### 2021-12-10 Slides.Rmd
Fixed up

\tiny
```{r, echo=FALSE}
data_no_catchers <- usable_data[, -18]

@@

```{r, cache=T}
x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike

@@

```{r, cache=TRUE, message=FALSE}
#LASSO
lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')

>>>>

```{r, echo=FALSE}
data_no_catchers <- usable_data[, -18]

@@

```{r}
x <- model.matrix(strike ~ ., data = data_no_catchers)[, -1]
y <- data_no_catchers$strike

@@

```{r, message=FALSE}
#LASSO
lasso_fit <- glmnet(x[train, ], y[train], alpha = 1, lambda = lambda, family = 'binomial')
cv_lasso <- cv.glmnet(x[train, ], y[train], alpha = 1, family='binomial')
